Marshall and Olkin-G and Gamma-G family of distribution: properties and applications

### 2022-05-25 paper/letter_answers.tex
Add TTT plots.

@@

2 -- The expression (3.1) in page 6 corresponds to the log-likelihood of
a MO-\(\Gamma\)-\(G\) distribution, considering a Weibull distribution
for \(G\) (although there is an error in the last sum of line 1), not a
general distribution with a \(\eta\) vector of parameters. Therefore,
the text or the expression should be written accordingly.

@@

\emph{Response}:
\textcolor{red}{Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis. What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}

\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.
Indeed, the way in which the application section was written suggests that an attempt was made to fix the $G\sim Weibull$ distribution as one of the necessary assumptions for the analysis. What actually happened is that for the datasets used, the Weibull distribution appeared to be a suitable distribution.}

\textcolor{red}{In order to remove some ambiguity, we opted to extend the simulation studies, where we also include the simulations, considering $G\sim Weibull$.}

@@

\emph{Response}:
\textcolor{red}{Thanks for the observation. The Dagum distribution was included in Table 1.}

5 -- As the \texttt{goodness.fit} function gives several statistics, the
authors should justify why they only chose the Anderson Darling and
Cramer-von Mises statistics.

\emph{Response}:
\textcolor{red}{The use of the $A^*$ and $W^*$ statistics, Anderson-Darling and Cramer-von Mises statistics, respectively, corrected by Chen and Balakrishnan, in the paper entitled "A General Purpose Approximate Goodness-of-Fit Test" (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) are suitable for comparing models that are not necessarily embedded. Therefore, considering the statistics returned by the \texttt{goodness.fit} function and considering the distributions compared, we understand that the statistics $A^*$ and $W^*$ are the most suitable for making the comparisons.}

\textcolor{red}{The  \textbf{AdequacyModel} package was developed by one of the authors of this paper and was published at   \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. A code inspection of the \texttt{goodness.fit} function can be done by looking at the   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}

@@

@@

\emph{Response}:
\textcolor{red}{Thanks for the sugestion. The change suggestion has been implemented.}

@@

@@

@@

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \tightlist
  \item
    \textcolor{red}{Really, the title of the paper was really bad. We switched to \textbf{Marshall and Olkin-G and Gamma-G family of distribution: properties and applications}. We believe that the title now clarifies the paper's proposal better.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textcolor{red}{Change made. Thanks for the sugestion.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \textcolor{red}{Thanks for the observation. The presentation of tables has been reorganized.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{3}
  \tightlist
  \item
    \textcolor{red}{Thanks for the sugestion.We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the
    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
  \end{enumerate}
\end{itemize}

\closing{Kind regards,}

>>>>

\textcolor{red}{Thank you. Done}.

@@

2 -- The expression (3.1) in page 6 corresponds to the log-likelihood of the MO-\(\Gamma\)-\(G\) distribution, 
thus considering a Weibull distribution
for \(G\) (although there is an error in the last sum 
of line 1), not a general distribution with a \(\eta\) 
vector of parameters. Therefore, the text or the expression 
should be written accordingly.

@@

\emph{Response}:
\textcolor{red}{Indeed, the way in which the application section was introduced suggests that an attempt was made to fit the $G\sim Weibull$ model as a suitable distribution to the current datasets. In order to remove some ambiguity, we opted to extend the simulation studies, where we now include the $G\sim Weibull$ in the simulations.}

@@

\emph{Response}:
\textcolor{red}{Thank you for pointing that out. The Dagum distribution was now included in Table 1.}

5 -- As the \texttt{goodness.fit} function gives several statistics, the authors should justify why they only chose the Anderson Darling and Cram\'er-von Mises statistics.

\emph{Response}:
\textcolor{red}{The use of the Anderson-Darling  $A^*$ and Cram\'er-von Mises $W^*$  statistics, corrected by Chen and Balakrishnan, in the paper entitled ``A General Purpose Approximate Goodness-of-Fit Test'' (see   \url{https://www.tandfonline.com/doi/abs/10.1080/00224065.1995.11979578}) is indicated for comparing mo\-dels that are not necessarily embedded. Hence, considering the statistics returned by the \texttt{goodness.fit} function and the distributions compared, we understand that these statistics are the most suitable ones for 
the comparisons.}

\textcolor{red}{The \textbf{AdequacyModel} package was developed 
by one of the authors of this paper and it was published at   \url{https://journals .plos.org/plosone/article?id=10.1371/journal.pone.0221487}. 
A code inspection of the \texttt{goodness.fit} function can be done by looking at the link   \href{https://github.com/prdm0/AdequacyModel/blob/master/R/goodness.fit.R}{link} on GitHub, where it is hosted the development versioning of the package.}

@@

\emph{Response}: \textcolor{red}{Done.}

@@

\emph{Response}:
\textcolor{red}{Thanks for the suggestion. The change suggestion has been implemented.}

@@

\textcolor{red}{We have improved the English language of the article in all sections.}

@@

\textcolor{red}{The Marshall and Olkin-G and Gamma-G generators, each with one more parameter, are often used to build new distributions. We empirically show through two real datasets that by combining these two generators, we obtain a new family of distributions that is better than two families widely used in the literature: beta and Kumarawamy (each one of the three with two parameters). In fact, the ``beta-G family of distributions" has over 3100 citations on google, whereas the ``Kumaraswamy-G family of distributions" has over 4500 citations  up to this date (May, 2022). Further, the properties of the proposed family are obtained similarly from the other two families using exponentiated distributions.}

@@

\begin{itemize}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \tightlist
  \item
    \textcolor{red}{ Really, the title of the paper was no good. We changed to \textbf{Marshall and Olkin-Gamma-G family of distributions: properties and applications}. We believe that the title now clarifies the paper's proposal better. It is worth mentioning that the new name is consistent with the sequential application of the MO family to the baseline Gamma-G.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{1}
  \tightlist
  \item
    \textcolor{red}{Done. Thanks for the suggestion.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{2}
  \tightlist
  \item
    \textcolor{red}{Thanks for this point. The presentation of the tables was reorganized.}
  \end{enumerate}
\item
  \begin{enumerate}
  \def\labelenumi{(\roman{enumi})}
  \setcounter{enumi}{3}
  \tightlist
  \item
    \textcolor{red}{Thanks for the suggestion. We chose to put the code for the simulations in a repository on GitHub. Thus, we considerably reduced the number of pages in the article and made it easier for readers of the material to reuse the code. With the code on GitHub it is also possible to verify the implementation and validate the simulations obtained. To access the codes, see the link 
    \url{https://github.com/prdm0/MOGG/tree/master/code/simulations}}.
  \end{enumerate}
\end{itemize}

\closing{Yours Sincerely,}
